A survey of HTTP caching options on the open Web

### 2015-01-13 sanity/paper1.tex
Add footnotes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@969 43ef1190-90fd-4dd7-a769-d0121f02b80e

We find that only one SPARQL Endpoint yields a heuristic lifetime, on
closer inspection, we find this to be hosted by Dydra\todo{ref?}. We
speculate that this is due to that few underlying DBMS systems help
track modification times in a way that can be used on a SPARQL result
basis.

@@

The Billion Triple Challenge 2014 dataset provided data in the form of
NQuad files. Due to the presence of invalid RDF, we iterated through
the NQuad files on a line-by-line basis. First, we matched each line
against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework RDF::Trine\todo{footnote} was used to parse the
line. Lines that failed to parse was discarded. We have not
investigated whether this could introduce biases. Statements were then
accepted into a new NQuad file if they had a predicate that matched
the \rdfterm{sd:endpoint}\todo{footnote} or matched a case-insensitive
regular expression \texttt{sparql} if the subject and objects were
both resources, or the predicates \rdfterm{void:vocabulary},
\rdfterm{rdfa:vocabulary} or \rdfterm{api:vocabulary} \todo{footnotes
  for all}, as well as having an resource as object. Finally,
statements with the the classes \rdfterm{cogs:Endpoint},
\rdfterm{owl:Ontology} and \rdfterm{voaf:Vocabulary} \todo{footnotes
  for all} in the object position were also accepted. More classes and
properties were considered, but not used in the data reduction if they
did not occur in the original data.

@@

\begin{table}
\caption{Recorded HTTP headers}\label{tab:headers}
 \begin{tabular}{ | l |  p{3cm} | p{5cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogates} & Edge Architecture Specification\cite{edgearch} & Draft
to allow more fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww\todo{ref}  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww\todo{ref}  & Header inserted by User
Agent to give details about problems with the download \\ \hline

>>>>

We find that only one SPARQL Endpoint yields a heuristic lifetime, on
closer inspection, we find this to be hosted by
Dydra\footnote{http://dydra.com/}. We speculate that this is due to
that few underlying DBMS systems help track modification times in a
way that can be used on a SPARQL result basis.

@@

The Billion Triple Challenge 2014 dataset provided data in the form of
NQuad files. Due to the presence of invalid RDF, we iterated through
the NQuad files on a line-by-line basis. First, we matched each line
against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework
RDF::Trine\footnote{https://metacpan.org/release/GWILLIAMS/RDF-Trine-1.011} was used
to parse the line. Lines that failed to parse was discarded. We have
not investigated whether this could introduce biases. Statements were
then accepted into a new NQuad file if they had a predicate that
matched the
\rdfterm{sd:endpoint}\footnote{http://www.w3.org/TR/sparql11-service-description/#sd-endpoint}
or matched a case-insensitive regular expression \texttt{sparql} if
the subject and objects were both resources, or the predicates
\rdfterm{void:vocabulary}\footnote{http://www.w3.org/TR/void/#vocabularies},
\rdfterm{rdfa:vocabulary}\footnote{http://www.w3.org/TR/rdfa-core/#term-prefix-definitions-vocabulary}
or
\rdfterm{api:vocabulary}\footnote{http://purl.org/linked-data/api/vocab#vocabulary},
as well as having an resource as object. Finally, statements with the
the classes
\rdfterm{cogs:Endpoint}\footnote{http://vocab.deri.ie/cogs#Endpoint},
\rdfterm{owl:Ontology} and
\rdfterm{voaf:Vocabulary}\footnote{http://lov.okfn.org/vocab/voaf/v2.3/index.html#Vocabulary}
in the object position were also accepted. More classes and properties
were considered, but not used in the data reduction if they did not
occur in the original data.

@@

\begin{table}
\caption{Recorded HTTP headers}\label{tab:headers}
 \begin{tabular}{ | l |  p{3cm} | p{5cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogates} & Edge Architecture Specification\cite{edgearch} & Draft
to allow more fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww\footnote{https://metacpan.org/release/GAAS/libwww-perl-6.04}  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww  & Header inserted by User
Agent to give details about problems with the download \\ \hline
